Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2014-08-20 chFabryPerot/chapter-fabryperot.tex
organize the chapters into folders with their figures

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=HyeonjuTrans.pdf, width=\textwidth}
\caption[Hyeonju's transmission experiment]{Hyeonju's measurement of transmission as a function of wavelength for bonded Silicon pucks in the wavelength range $1500 < \lambda \textrm{(nm)} < 2500 $.  Hyeonju made the measurement with the CROWBAR on August 19, 2011.  The bonded Si pucks and double side polished reference puck show transmission indistinguishable within the uncertainty of the signal to noise $\sim5$ measurement.}
\label{fig:hyeonju-trans}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=Etalon, width=0.5\textwidth}
\caption[Etalon schematic]{Schematic of reflection and transmission at the interfaces of an etalon.  Our experiment involves an air gap sandwiched between two Si walls.  The reflectance of the Si walls originates from the sharp transition of refractive index, so called Fresnel reflection.  This figure is copied from Wikipedia, it is licensed under Creative Commons Attribution-ShareAlike 3.0 License by author Kevin Morse.}
\label{fig:etalon}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=Cary-gully-trans.pdf, width=0.88\textwidth}
\caption[Cary 5000 transmission]{Transmission of the bonded pucks HA1$-$HA2, the pucks Hyeonju Jeong bonded in 2011.  Also shown is a reference double side polished silicon puck.  Each piece was measured twice.  The repeated measurement lines are mostly indiscernible from the thick lines used for presentation on these high signal to noise ratio, high dynamic range measurements.  The transmission of the reference puck clearly differs from the bonded puck.  Atmospheric absorption degrades measurements at wavelengths greater than 2500 nm.  It is a mystery why the transmission exceeds the Fresnel prediction.}
\label{fig:Cary500}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=FabPerot-gully-trans.pdf, width=0.92\textwidth}
\caption[Fabry-P\`{e}rot model of HA1$-$HA2]{Small ($<10\%$) transmission losses attributable to the gap are clearly distinguishable from measurement uncertainty.  Modeling of the gap as a Fabry-P\`{e}rot etalon with a uniform gap over the $\sim 12 \textrm{ mm } \times 20\textrm{ mm }$ area reveals an average gap size of 41 nm.  Models of 30 and 50 nm gaps are clearly rejected based on the measurement uncertainty.  The precipitous drop off at 1100 nm is from Si absorption.}
\label{fig:FabPerotHA1HA2}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=bonded-wafer-holder-pic.png, width=0.5\textwidth}
\caption[Cary 5000 sample size]{A photo of the Cary 5000 sample holder.  The area is about 12 mm $\times$ 20 mm.  At the time of writing it is not known if the beam is uniform over that area.  Hyeonju's bonded Si wafer A is taped to the sample holder.}
\label{fig:Cary5000sampleArea}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=gully-Si-wafers-transmission.pdf, width=1.0\textwidth}
\caption[Bonded Si wafer transmission]{This graphic demonstrates a few key aspects of our measurements, which I will describe the in order of magnitude of the effect.  First, the transmission of Si wafers exceeds the prediction for Fresnel reflection (dashed curve) by 5\% (i.e. 10\% of the $\sim$50\% signal, or about 20$\sigma$).  This discrepancy is a mystery, we speculate about its origin in later sections.  Second, the bonded wafer puck is clearly separated from the DSP reference samples.  Third, the systematic error from repeatability from two different days is perceptible by the top red curve and its companion dashed red curve a half percent below.  Lastly, all the wafers, whether bonded or not, demonstrate indistinguishable transmission properties, which is evidence for negligible gap in the bonded wafers.}
\label{fig:Cary5000wafer}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=gully-Si-wafers-fabperot.pdf, width=1.0\textwidth}
\caption[Fabry-P\`{e}rot model shows $<4$ nm gaps in wafers]{The average measured transmission of bonded Si wafers compared to three Fabry-P\`{e}rot models for air gaps of 0, 4, 12 nm.  A gap width of 12 nm is ruled out at over 5$\sigma$.}
\label{fig:Wafers4nmGap}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=VG03_pattern.pdf, width=0.82\textwidth}
\caption[VG03 Pattern]{This is a detail of the pattern on the surface of VG03.  The depth is about 4000 nm.}
\label{fig:VG03pattern}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=VG04_detail.pdf, width=\textwidth}
\caption[VG04 Detail]{Detail of the pattern and its location in VG04.  Measurement locations are marked 1 and 2 in the photo at the right.  Position 1 is roughly at the location of the of the pattern, while position 2 is in an area that should be fully contacted (no gaps). }
\label{fig:VG04detail}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=VG03_PDF.pdf, width=0.5\textwidth}
\caption[VG03 Schematic]{We marked the location of the 4000 nm divot with a permanent marker while it was imaged with the IR mask aligner.  We are confident that the measurement box was fully encapsulated in the divot.}
\label{fig:VG03schematicl}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=VG03_1and2.pdf, width=0.95\textwidth}
\caption[VG03 Transmission]{Transmission spectra of VG03 in positions 1 and 2.}
\label{fig:VG03transl}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=VG02.pdf, width=0.5\textwidth}
\caption[VG02 measurement position layout]{Measurement layout of VG02}
\label{fig:VG02layout}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=VG02_1to4.pdf, width=0.95\textwidth}
\caption[VG02 transmission in 4 position]{Transmission as measured in 4 distinct sub-apertures of VG02.}
\label{fig:VG02trans}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=VG02_pos1hist.pdf, width=0.48\textwidth}
\ \psfig{file=VG02_pos4hist.pdf, width=0.48\textwidth}
\caption[VG02 gap size distribution]{A gap size distribution consistent with the measured transmission spectrum of VG02 positions 1 and 4}
\label{fig:VG02gapDist}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=VG01.pdf, width=0.65\textwidth}
\caption[VG01 transmission]{Measured transmission of VG01 is consistent with no, or negligible air gap.}
\label{fig:VG01trans}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=VG04.pdf, width=0.85\textwidth}
\caption[VG04 transmission]{Measured transmission of VG04 demonstrates a larger gap ($\sim550$ nm) than anticipated ($\sim15-25$ nm).  }
\label{fig:VG04trans}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=fresnel_Si_index.pdf, width=0.5\textwidth}
\caption[Fresnel prediction]{The Fresnel prediction for Si transmission is 90\% of the transmission measured.  The discrepancy persists despite any unreasonable estimate of temperature.  It would take changing the Si refractive index to an unreasonable value of about 3.2 in order to boost the post-dicted Fresnel transmission model to the observed value.}
\label{fig:Fresneldiscrepancy}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=Si_index_temp, width=\textwidth}
\caption[Si temperature has negligible effect on Fabry-P\`{e}rot]{The ambient temperature will have no measurable impact on the Fabry-P\`{e}rot transmission.}
\label{fig:SiTempFP}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=1523_fabperot.pdf, width=0.8\textwidth}
\caption[Monochromatic Fabry-P\`{e}rot at 1523 nm]{Expected transmission as a function of gap size for a fixed wavelength- a 1523 nm HeNe laser.}
\label{fig:1523nmFP}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=20130502_baseline.pdf}
\caption[Cary 5000 raw spectrum]{Raw spectrum of the Cary 5000.  The black line is the mean of six 100\% baseline scans sampled over 2 hours.  The red filled band defines the maximum and minimum bounds at each spectral sample.}
\label{fig:Cary5000baseline}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=cary5000_beam_notitle.pdf}
\caption[Cary 5000 beam size]{Beam size analysis of the Cary 5000 based on measurements of 7 custom circular apertures.  }
\label{fig:Cary5000beam}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=cary5000_linearity_notitle.pdf}
\caption[Cary 5000 linearity plot]{This figure demonstrates the high degree of linearity of the Cary 5000.  The measured value is indistinguishable from the predicted value down to 24 dB.  The error bars are plotted but are imperceptible from the symbols.  There is a minuscule and likely negligible excess of measured flux at the lowest flux measurements.}
\label{fig:Cary5000linearity}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=Cary5000polarizer.pdf, width=\textwidth}
\caption[Cary 5000 Polarizer Setup]{Schematic of the Cary 5000 setup to handle polarizing samples.  The graphic is from the Cary 5000 Polarization mode data sheet, which is reprinted in its entirety in Appendix section \ref{sec:A2Cary5000Pol}}
\label{fig:Cary5000Polarizer}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=SiTransAng_notitle.pdf, width=\textwidth}
\caption[Angular dependent Si transmission]{Angular dependent Si transmission as measured by the Cary 5000 (top dashed or dotted curves), and predicted from Fresnel transmission theory for unpolarized incident light (bottom gray curves).}
\label{fig:AngularSiTrans}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=20130502_mult_fresnel.pdf}
\caption[Multiple incoherent internal reflections in a Si puck]{Multiple incoherent internal reflections in a Si puck with parallel surfaces.  The red curve is the transmission spectrum of DSP Si wafer VG05 at normal incidence measured with the Cary 5000.  The blue dash-dot curve is the modeled Fresnel transmission spectrum ignoring multiple internal reflections.  The black dotted line matches the measured transmission spectrum much better because the black dotted line includes multiple internal reflections within the Si wafer.  The measurement error is comparable to the thickness of the line in this high signal to noise measurement.  Still, there is evidence for a dearth of measured flux compared to the prediction with multiple reflections.  The amplitude of the flux deficit ranges from $1-6\; \sigma$ (with $\sigma=\sigma_{sys}=0.002$ from $\lambda=$ 2500 $-$ 1100 nm.  The wavelength dependence hints at scattered light as the origin.}

>>>>

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/HyeonjuTrans.pdf, width=\textwidth}
\caption[Hyeonju's transmission experiment]{Hyeonju's measurement of transmission as a function of wavelength for bonded Silicon pucks in the wavelength range $1500 < \lambda \textrm{(nm)} < 2500 $.  Hyeonju made the measurement with the CROWBAR on August 19, 2011.  The bonded Si pucks and double side polished reference puck show transmission indistinguishable within the uncertainty of the signal to noise $\sim5$ measurement.}
\label{fig:hyeonju-trans}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/Etalon.png, width=0.5\textwidth}
\caption[Etalon schematic]{Schematic of reflection and transmission at the interfaces of an etalon.  Our experiment involves an air gap sandwiched between two Si walls.  The reflectance of the Si walls originates from the sharp transition of refractive index, so called Fresnel reflection.  This figure is copied from Wikipedia, it is licensed under Creative Commons Attribution-ShareAlike 3.0 License by author Kevin Morse.}
\label{fig:etalon}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/Cary-gully-trans.pdf, width=0.88\textwidth}
\caption[Cary 5000 transmission]{Transmission of the bonded pucks HA1$-$HA2, the pucks Hyeonju Jeong bonded in 2011.  Also shown is a reference double side polished silicon puck.  Each piece was measured twice.  The repeated measurement lines are mostly indiscernible from the thick lines used for presentation on these high signal to noise ratio, high dynamic range measurements.  The transmission of the reference puck clearly differs from the bonded puck.  Atmospheric absorption degrades measurements at wavelengths greater than 2500 nm.  It is a mystery why the transmission exceeds the Fresnel prediction.}
\label{fig:Cary500}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/FabPerot-gully-trans.pdf, width=0.92\textwidth}
\caption[Fabry-P\`{e}rot model of HA1$-$HA2]{Small ($<10\%$) transmission losses attributable to the gap are clearly distinguishable from measurement uncertainty.  Modeling of the gap as a Fabry-P\`{e}rot etalon with a uniform gap over the $\sim 12 \textrm{ mm } \times 20\textrm{ mm }$ area reveals an average gap size of 41 nm.  Models of 30 and 50 nm gaps are clearly rejected based on the measurement uncertainty.  The precipitous drop off at 1100 nm is from Si absorption.}
\label{fig:FabPerotHA1HA2}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/bonded-wafer-holder-pic.png, width=0.5\textwidth}
\caption[Cary 5000 sample size]{A photo of the Cary 5000 sample holder.  The area is about 12 mm $\times$ 20 mm.  At the time of writing it is not known if the beam is uniform over that area.  Hyeonju's bonded Si wafer A is taped to the sample holder.}
\label{fig:Cary5000sampleArea}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/gully-Si-wafers-transmission.pdf, width=1.0\textwidth}
\caption[Bonded Si wafer transmission]{This graphic demonstrates a few key aspects of our measurements, which I will describe the in order of magnitude of the effect.  First, the transmission of Si wafers exceeds the prediction for Fresnel reflection (dashed curve) by 5\% (i.e. 10\% of the $\sim$50\% signal, or about 20$\sigma$).  This discrepancy is a mystery, we speculate about its origin in later sections.  Second, the bonded wafer puck is clearly separated from the DSP reference samples.  Third, the systematic error from repeatability from two different days is perceptible by the top red curve and its companion dashed red curve a half percent below.  Lastly, all the wafers, whether bonded or not, demonstrate indistinguishable transmission properties, which is evidence for negligible gap in the bonded wafers.}
\label{fig:Cary5000wafer}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/gully-Si-wafers-fabperot.pdf, width=1.0\textwidth}
\caption[Fabry-P\`{e}rot model shows $<4$ nm gaps in wafers]{The average measured transmission of bonded Si wafers compared to three Fabry-P\`{e}rot models for air gaps of 0, 4, 12 nm.  A gap width of 12 nm is ruled out at over 5$\sigma$.}
\label{fig:Wafers4nmGap}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/VG03_pattern.pdf, width=0.82\textwidth}
\caption[VG03 Pattern]{This is a detail of the pattern on the surface of VG03.  The depth is about 4000 nm.}
\label{fig:VG03pattern}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/VG04_detail.pdf, width=\textwidth}
\caption[VG04 Detail]{Detail of the pattern and its location in VG04.  Measurement locations are marked 1 and 2 in the photo at the right.  Position 1 is roughly at the location of the of the pattern, while position 2 is in an area that should be fully contacted (no gaps). }
\label{fig:VG04detail}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/VG03_PDF.pdf, width=0.5\textwidth}
\caption[VG03 Schematic]{We marked the location of the 4000 nm divot with a permanent marker while it was imaged with the IR mask aligner.  We are confident that the measurement box was fully encapsulated in the divot.}
\label{fig:VG03schematicl}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/VG03_1and2.pdf, width=0.95\textwidth}
\caption[VG03 Transmission]{Transmission spectra of VG03 in positions 1 and 2.}
\label{fig:VG03transl}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/VG02.pdf, width=0.5\textwidth}
\caption[VG02 measurement position layout]{Measurement layout of VG02}
\label{fig:VG02layout}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/VG02_1to4.pdf, width=0.95\textwidth}
\caption[VG02 transmission in 4 position]{Transmission as measured in 4 distinct sub-apertures of VG02.}
\label{fig:VG02trans}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/VG02_pos1hist.pdf, width=0.48\textwidth}
\ \psfig{file=chFabryPerot/VG02_pos4hist.pdf, width=0.48\textwidth}
\caption[VG02 gap size distribution]{A gap size distribution consistent with the measured transmission spectrum of VG02 positions 1 and 4}
\label{fig:VG02gapDist}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/VG01.pdf, width=0.65\textwidth}
\caption[VG01 transmission]{Measured transmission of VG01 is consistent with no, or negligible air gap.}
\label{fig:VG01trans}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/VG04.pdf, width=0.85\textwidth}
\caption[VG04 transmission]{Measured transmission of VG04 demonstrates a larger gap ($\sim550$ nm) than anticipated ($\sim15-25$ nm).  }
\label{fig:VG04trans}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/fresnel_Si_index.pdf, width=0.5\textwidth}
\caption[Fresnel prediction]{The Fresnel prediction for Si transmission is 90\% of the transmission measured.  The discrepancy persists despite any unreasonable estimate of temperature.  It would take changing the Si refractive index to an unreasonable value of about 3.2 in order to boost the post-dicted Fresnel transmission model to the observed value.}
\label{fig:Fresneldiscrepancy}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/Si_index_temp, width=\textwidth}
\caption[Si temperature has negligible effect on Fabry-P\`{e}rot]{The ambient temperature will have no measurable impact on the Fabry-P\`{e}rot transmission.}
\label{fig:SiTempFP}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/1523_fabperot.pdf, width=0.8\textwidth}
\caption[Monochromatic Fabry-P\`{e}rot at 1523 nm]{Expected transmission as a function of gap size for a fixed wavelength- a 1523 nm HeNe laser.}
\label{fig:1523nmFP}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/20130502_baseline.pdf}
\caption[Cary 5000 raw spectrum]{Raw spectrum of the Cary 5000.  The black line is the mean of six 100\% baseline scans sampled over 2 hours.  The red filled band defines the maximum and minimum bounds at each spectral sample.}
\label{fig:Cary5000baseline}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/cary5000_beam_notitle.pdf}
\caption[Cary 5000 beam size]{Beam size analysis of the Cary 5000 based on measurements of 7 custom circular apertures.  }
\label{fig:Cary5000beam}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/cary5000_linearity_notitle.pdf}
\caption[Cary 5000 linearity plot]{This figure demonstrates the high degree of linearity of the Cary 5000.  The measured value is indistinguishable from the predicted value down to 24 dB.  The error bars are plotted but are imperceptible from the symbols.  There is a minuscule and likely negligible excess of measured flux at the lowest flux measurements.}
\label{fig:Cary5000linearity}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/Cary5000polarizer.pdf, width=\textwidth}
\caption[Cary 5000 Polarizer Setup]{Schematic of the Cary 5000 setup to handle polarizing samples.  The graphic is from the Cary 5000 Polarization mode data sheet, which is reprinted in its entirety in Appendix section \ref{sec:A2Cary5000Pol}}
\label{fig:Cary5000Polarizer}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/SiTransAng_notitle.pdf, width=\textwidth}
\caption[Angular dependent Si transmission]{Angular dependent Si transmission as measured by the Cary 5000 (top dashed or dotted curves), and predicted from Fresnel transmission theory for unpolarized incident light (bottom gray curves).}
\label{fig:AngularSiTrans}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chFabryPerot/20130502_mult_fresnel.pdf}
\caption[Multiple incoherent internal reflections in a Si puck]{Multiple incoherent internal reflections in a Si puck with parallel surfaces.  The red curve is the transmission spectrum of DSP Si wafer VG05 at normal incidence measured with the Cary 5000.  The blue dash-dot curve is the modeled Fresnel transmission spectrum ignoring multiple internal reflections.  The black dotted line matches the measured transmission spectrum much better because the black dotted line includes multiple internal reflections within the Si wafer.  The measurement error is comparable to the thickness of the line in this high signal to noise measurement.  Still, there is evidence for a dearth of measured flux compared to the prediction with multiple reflections.  The amplitude of the flux deficit ranges from $1-6\; \sigma$ (with $\sigma=\sigma_{sys}=0.002$ from $\lambda=$ 2500 $-$ 1100 nm.  The wavelength dependence hints at scattered light as the origin.}
